\section{Results \& Evaluation}\label{results}

% Results are often presented in tables, figures and other relevant illustrations. Include text that refers to these figures/tables. 

\subsection{Evaluation Process}
For the first round of app evaluation, 5 users who were women between the ages of 30 and 65 were recruited to watch a demo video of the app and fill out a SUS and a few long answer questions with their feedback. These participants were recruited via email and were asked to read throguh a participant information sheet before participating.

\begin{table}[h!!]
    \begin{tabular}{ll}
    \hline
    SUS Scores(n=5) &      \\ \hline
                    & 67.5 \\
                    & 85   \\
                    & 72.5 \\
                    & 77.5 \\
                    & 65   \\
        Average Score & 73.5
    \end{tabular}
    \end{table}

From the average SUS score of 73.5, it is clear that the app is usable as its in the top 27\% of scores, but it could be improved.

After obtaining these results, changes were made to the apps look and feel and included more instructions. AB Testing was then conductd with more participants to see if the changes made had a positive impact on the SUS score. 

**Will put results here** 

The app was then rated according to the MARS rating system and compared to the other app rated at the beginning of the study. **Results here** 

\subsection{Results of Evaluation}
This Section includes a direct interpretation of the gathered data and evaluation processes. 

\subsection{Returning to the Research Questions}
Return to research questions or objectives as appropriate. 

\subsubsection{RQ1}
It is clear from our findings that James Bond was born in Wigtown in Scotland. However, he grew up in Diss, in Norfolk. 
We know this because ....


\subsubsection{RQ2}
We were not able to answer this question from our studies, although some suggestions were made. These could not be proven. 

\subsubsection{Objective 1}


\subsubsection{Objective 2}